Landscape composition and beneficial insects

### 2020-04-16 manuscript/manuscript_outline.Rmd
Created correlation plots, and started looking into multicollinearity

* Point estimates of abundance are influenced by spatio-temporal processes 
  + Arthropods move between landscape components depending on their life history
  + e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields (Desender and Alderweireldt 1988, J. of App. Ent.)
  + Counts are a proxy of activity density, not necessarily abundance
  + Nevertheless, this is an OK measure (_need to justify this_)

@@

* We used a system of pitfall traps located in southern Alberta in 2017

>>>>

* Point estimates of abundance are influenced by spatio-temporal processes 
  + Arthropods move between landscape components depending on their life history
  + e.g. Carabid beetles are thought to reproduce in field margins, but adults feed in fields (Desender and Alderweireldt 1988, J. of App. Ent.)
  + Counts are a proxy of activity density, not necessarily abundance
  + Nevertheless, this is probably an OK measure (_need to justify this_)

@@

##Data collection

* We used a system of pitfall traps installed in ditches, field margins, wetlands, and in-field sites across southern Alberta in 2017 (_need a map here_)
  + Traps at in-field sites were installed 20, 100, 200m (?) along a transect from the nearest non-crop feature (wetland, grassland, pivot)
  +

* To characterize landscape composition surrounding the traps, we used classified landscape data from AAFC
  + Classifications are very accurate for fields (~90%), but less accurate for non-crop areas (~70%)
  + Landscape studies often use the landscape composition within a circle of a fixed radius surrounding each point
  + However, the radius of the circle depends on the grain of the landscape that is relevant to the abundance of a given organism.
  + We used a novel method 
  + Instead, we divided the landscape into annuli (rings) surrounding each trap location.
  + Each annulus was 30 m thick, and had inner radii ranging from 30 to 1470m, in increments of 30m.

##Statistics
